Laplacian envelope

### 2021-07-29 Notes/laplace.tex
topology constraints

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage[tables,graphics,draft]{sl-preamble}
% \usepackage{stix}
%\usepackage{amsldoc} for finding documentation only
\def\Snospace~{\S{}}
\renewcommand{\sectionautorefname}{\Snospace}
\renewcommand{\subsectionautorefname}{\Snospace}
\renewcommand{\subsubsectionautorefname}{\Snospace}
%
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%================================================================================
\makeatletter
\DeclareFontEncoding{LS2}{}{\noaccents@}
\makeatother

\DeclareFontSubstitution{LS2}{stix}{m}{n}
\DeclareSymbolFont{xlargesymbols}{LS2}{stixex}{m}{n}
\DeclareMathDelimiter{\lAngle}{\mathopen}{xlargesymbols}{"EC}{xlargesymbols}{"12}
\DeclareMathDelimiter{\rAngle}{\mathclose}{xlargesymbols}{"ED}{largesymbols}{"13}
\DeclareMathDelimiter{\lVvert}{\mathopen}{xlargesymbols}{"F2}{xlargesymbols}{"F5}
\DeclareMathDelimiter{\rVvert}{\mathclose}{xlargesymbols}{"F2}{xlargesymbols}{"F5}

\newcommand{\aav}[1]{\mathopen{}\left\lAngle #1 \right\rAngle\mathclose{}}
\newcommand{\nnrm}[1]{\mathopen{}\left\lVvert #1 \right\rVvert\mathclose{}}
%================================================================================
%
% \usepackage{adjustbox}
% \newcommand{\aligntop}[1]{\adjustbox{valign=t}{#1}}
% \newcommand{\alignmid}[1]{\adjustbox{valign=c}{#1}}
%
\usepackage{paralist}
\newenvironment{myenuma}{\begin{inparaenum}[(a)]}{\end{inparaenum}}
\newenvironment{myenumi}{\begin{inparaenum}[i)]}{\end{inparaenum}}
\newenvironment{myenumA}{\begin{inparaenum}[\bfseries A.]}{\end{inparaenum}}
\newenvironment{myenumI}{\begin{inparaenum}[\bfseries I.]}{\end{inparaenum}}
\newenvironment{myenumr}{\begin{inparaenum}[1.]}{\end{inparaenum}}
%for nested lists, \ref only produces innermost item:  (hacky)
\makeatletter % for internal macros with @
\renewcommand\p@enumii{}
\makeatother
%
%================================================================================
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MMm}{Q}
\newcommand{\MM}{\mathbf{\MMm}}
%prob distribution
\newcommand{\prm}{p}
\newcommand{\pr}{\mathbf{\prm}}
%equilibrium distribution
\newcommand{\eqm}{\pi}
\newcommand{\eq}{\boldsymbol{\eqm}}
%equilibrium metric
\newcommand{\Eqm}{\Pi}
\newcommand{\Eq}{\boldsymbol{\Eqm}}
%first passage times
\newcommand{\fptm}{T}
\newcommand{\fpt}{\mathbf{\fptm}}
%off-diag first passage times
\newcommand{\fptbm}{\overline{\fptm}}
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fundm}{Z}
\newcommand{\fund}{\mathbf{\fundm}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arowm}{\xi}
\newcommand{\arow}{\boldsymbol{\arowm}}
\newcommand{\Lbm}{\Lambda}
\newcommand{\Lb}{\boldsymbol{\Lbm}}
\newcommand{\lbm}{\lambda}
\newcommand{\lb}{\boldsymbol{\lbm}}
\newcommand{\etwm}{\eta^w}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thbm}{\theta}
\newcommand{\thb}{\boldsymbol{\thbm}}
\newcommand{\ombm}{\omega}
\newcommand{\omb}{\boldsymbol{\ombm}}
\newcommand{\albm}{\alpha}
\newcommand{\alb}{\boldsymbol{\albm}}
%synapse models
\newcommand{\wm}{w}
\newcommand{\w}{\mathbf{\wm}}
\newcommand{\Wm}{W}
\newcommand{\W}{\mathbf{\Wm}}
\newcommand{\MMdm}{M}
\newcommand{\MMd}{\mathbf{\MMdm}}
\newcommand{\encm}{K}
\newcommand{\enc}{\mathbf{\encm}}
\newcommand{\frgm}{\Wm^{\mathrm{F}}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\Fm}{\Phi}
\newcommand{\F}{\boldsymbol{\Fm}}
%eigenvectors
\newcommand{\evrm}{u}
\newcommand{\evr}{\mathbf{\evrm}}
\newcommand{\evlm}{\eta}
\newcommand{\evl}{\boldsymbol{\evlm}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
% \newcommand{\CA}{\mathcal{A}}
% \newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

As discussed in \autoref{sec:recog}, the signal-to-noise ratio is given by
%
\begin{equation}\label{eq:SNRdef}
  \snr(t) = \frac{\av{\synid\cdt\syn(t)} - \av{\synid\cdt\syn(\infty)}}
     {\sqrt{\var(\synid\cdt\syn(\infty))}},
\end{equation}
%
Where the averages and variances are over the probability distribution of the synaptic states given the sequence of plasticity events, the probability distribution of the sequence of plasticity events themselves and the probability distribution of the pattern we are testing, \(\synid\).
If we also average over the time between storage and recognition, we have
%
\begin{equation}\label{eq:snrb}
  \snrb(\tau) = \intd[_0^\infty]{t} P(t\vert\tau) \snr(t)
   = \frac{1}{\tau} \intd[_0^\infty]{t} \e^{-t/\tau} \snr(t),
\end{equation}
%
This is similar to the average SNR up to time \(\tau\), but with the hard cut-off replaced with a smooth exponential.
This can be expressed in terms of he Laplace transform of the SNR curve in \eqref{eq:SNRdef}:
%
\begin{equation}\label{eq:laplacedef}
  A(s) = \intd[_0^\infty]{t} \e^{-st} \snr(t),
  \qquad
  \snrb(\tau) = \frac{A(1/\tau)}{\tau}.
\end{equation}
%

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s \I + \onev \arow -\MM)\inv,
\end{equation}
%
where \(\arow\) is an arbitrary row vector satisfying \(\arow \onev = \frac{1}{\tau_0} \neq 0\).
This reduces to the fundamental matrix at \(s=0\).
We can see that it obeys similar identities, including that \(\onev\) is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
\begin{aligned}
  \fund(s) \onev &= \frac{\tau_0}{1+s\tau_0}\onev, \qquad &
  \MM \fund(s) &= (\onev \eq - \I)(\I - s \fund), \\ 
  \arow \fund(s) &= \eq (\I - s \fund),  &
  \fund(s) \MM &= (\I - s \fund)(\tau_0 \onev \arow - \I).
\end{aligned}
\end{equation}
%
Suppose we have some row vector \(\mathbf{a}\) such that \(\mathbf{a}\onev=0\).
Then \(\mathbf{a}\fund(s)\) is independent of \(\arow\):
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\arowm_k} = -(\mathbf{a}\fund(s)\onev) \fundm_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fundm_{ki}(s) = 0.
\end{equation}
%

@@

At other values of \(s\) can they be interpreted as the mean first-passage times of a different process?
In order to have \cref{eq:lfund} as its fundamental matrix, the extra bit must draw probability from each state at a rate \(s\).
In other words, it should have the form \(s(\onev \boldsymbol{\zeta} - \I)\) for some \(\boldsymbol{\zeta} \) 
(which can be absorbed into \(\arow\) in \cref{eq:lfund}).
This other process must have the same steady-state distribution, so that its mean first-passage times are given by \cref{eq:lfptb}, so the probability drawn from each state must be redistributed proportional to \(\eq\).
This other stochastic process is
%
\begin{equation}\label{eq:lshift}
  \shift{\MM}(s) = \MM + s (\onev \eq - \I).
\end{equation}
%
This is a valid continuous-time Markov process.
Its fundamental matrix is given by \cref{eq:lfund} with \( \arow(s) = \arow + s \eq \) (although this last change is unnecessary).

This means that the \( \fptb(s) \) have all the same properties as in the case \(s=0\).
In particular, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptbm_{ij}(s) \eqm_j
\end{equation}
%
is independent of the starting state \(i\), but now \(\eta(s) = \tr\fund(s) - \frac{\tau_0}{1 + s \tau_0}\).
We can then define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptbm_{ij}(s) \eqm_j \prn{\frac{1 \pm \wm_j}{2}} 
      =  \sum_{j\in \pm} \fptbm_{ij}(s) \eqm_j.
\end{equation}
%
We can arrange the states in order of decreasing \(\eta^{+}_i(s)\) or increasing \(\eta^{-}_i(s)\).
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etwm_i(s) = \sum_j \fptbm_{ij}(s)\eqm_j \wm_j
    = \eta^+_i(s) - \eta^-_i(s) 
    = 2\eta^+_i(s) - \eta(s) 
    = \eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing \(\etwm_i(s)\) is the same as the order of decreasing \(\eta^{+}_i(s)\) or increasing \(\eta^{-}_i(s)\).
The \(\etwm_i(s)\) can still be used when \(\w\) takes more than two values.

@@

In analogy with the case \(s=0\), we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= \sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= \sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      = \sum_k \eqm_k {c}_k(s) \wm_k
      % = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) \wlg),s the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

@@

@@

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage[T1]{fontenc}
\usepackage{a4wide}
% \usepackage{stix2}
\usepackage[tables,graphics,draft,panels=paralist]{sl-preamble}
%\usepackage{amsldoc} for finding documentation only
\def\Snospace~{\S{}}
\renewcommand{\sectionautorefname}{\Snospace}
\renewcommand{\subsectionautorefname}{\Snospace}
\renewcommand{\subsubsectionautorefname}{\Snospace}
%
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%================================================================================
% \makeatletter
% \DeclareFontEncoding{LS2}{}{\noaccents@}
% \makeatother

% \DeclareFontSubstitution{LS2}{stix}{m}{n}
% \DeclareSymbolFont{xlargesymbols}{LS2}{stixex}{m}{n}
% \DeclareMathDelimiter{\lAngle}{\mathopen}{xlargesymbols}{"EC}{xlargesymbols}{"12}
% \DeclareMathDelimiter{\rAngle}{\mathclose}{xlargesymbols}{"ED}{largesymbols}{"13}
% \DeclareMathDelimiter{\lVvert}{\mathopen}{xlargesymbols}{"F2}{xlargesymbols}{"F5}
% \DeclareMathDelimiter{\rVvert}{\mathclose}{xlargesymbols}{"F2}{xlargesymbols}{"F5}

\newcommand{\aav}[1]{\mathopen{}\left\llangle #1 \right\rrangle\mathclose{}}
\newcommand{\nnrm}[1]{\mathopen{}\left\lWavy #1 \right\rWavy\mathclose{}}
%================================================================================
%
% \usepackage{adjustbox}
% \newcommand{\aligntop}[1]{\adjustbox{valign=t}{#1}}
% \newcommand{\alignmid}[1]{\adjustbox{valign=c}{#1}}
% %
% \usepackage{paralist}
% \newenvironment{myenuma}{\begin{inparaenum}[(a)]}{\end{inparaenum}}
% \newenvironment{myenumi}{\begin{inparaenum}[i)]}{\end{inparaenum}}
% \newenvironment{myenumA}{\begin{inparaenum}[\bfseries A.]}{\end{inparaenum}}
% \newenvironment{myenumI}{\begin{inparaenum}[\bfseries I.]}{\end{inparaenum}}
% \newenvironment{myenumr}{\begin{inparaenum}[1.]}{\end{inparaenum}}
% %for nested lists, \ref only produces innermost item:  (hacky)
% \makeatletter % for internal macros with @
% \renewcommand\p@enumii{}
% \makeatother
%
%================================================================================
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MMm}{Q}
\newcommand{\MM}{\mathbf{\MMm}}
%prob distribution
\newcommand{\prm}{p}
\newcommand{\pr}{\mathbf{\prm}}
%equilibrium distribution
\newcommand{\eqm}{\pi}
\newcommand{\eq}{\boldsymbol{\eqm}}
%equilibrium metric
\newcommand{\Eqm}{\Pi}
\newcommand{\Eq}{\boldsymbol{\Eqm}}
%first passage times
\newcommand{\fptm}{T}
\newcommand{\fpt}{\mathbf{\fptm}}
%off-diag first passage times
\newcommand{\fptbm}{\overline{\fptm}}
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fundm}{Z}
\newcommand{\fund}{\mathbf{\fundm}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arowm}{\xi}
\newcommand{\arow}{\boldsymbol{\arowm}}
\newcommand{\Lbm}{\Lambda}
\newcommand{\Lb}{\boldsymbol{\Lbm}}
\newcommand{\lbm}{\lambda}
\newcommand{\lb}{\boldsymbol{\lbm}}
\newcommand{\etwm}{\eta^w}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thbm}{\theta}
\newcommand{\thb}{\boldsymbol{\thbm}}
\newcommand{\ombm}{\omega}
\newcommand{\omb}{\boldsymbol{\ombm}}
\newcommand{\albm}{\alpha}
\newcommand{\alb}{\boldsymbol{\albm}}
\newcommand{\dgnm}{\zeta}
\newcommand{\dgn}{\boldsymbol{\dgnm}}
%synapse models
\newcommand{\wm}{w}
\newcommand{\w}{\mathbf{\wm}}
\newcommand{\Wm}{W}
\newcommand{\W}{\mathbf{\Wm}}
\newcommand{\MMdm}{M}
\newcommand{\MMd}{\mathbf{\MMdm}}
\newcommand{\encm}{K}
\newcommand{\enc}{\mathbf{\encm}}
\newcommand{\frgm}{\Wm^{\mathrm{F}}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\Fm}{\Phi}
\newcommand{\F}{\boldsymbol{\Fm}}
%eigenvectors
\newcommand{\evrm}{u}
\newcommand{\evr}{\mathbf{\evrm}}
\newcommand{\evlm}{\eta}
\newcommand{\evl}{\boldsymbol{\evlm}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
% \newcommand{\CA}{\mathcal{A}}
% \newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

As discussed in \cref{sec:recog}, the signal-to-noise ratio is given by
%
\begin{equation}\label{eq:SNRdef}
  \snr(t) = \frac{\av{\synid\cdt\syn(t)} - \av{\synid\cdt\syn(\infty)}}
     {\sqrt{\var(\synid\cdt\syn(\infty))}},
\end{equation}
%
Where the averages and variances are over the probability distribution of the synaptic states given the sequence of plasticity events, the probability distribution of the sequence of plasticity events themselves and the probability distribution of the pattern we are testing, \(\synid\).
If we also average over the time between storage and recognition, we have
%
\begin{equation}\label{eq:snrb}
  \snrb(\tau) = \intd[_0^\infty]{t} P(t\vert\tau) \snr(t)
   = \frac{1}{\tau} \intd[_0^\infty]{t} \e^{-t/\tau} \snr(t),
\end{equation}
%
This is similar to the average SNR up to time \(\tau\), but with the hard cut-off replaced with a smooth exponential.
This can be expressed in terms of he Laplace transform of the SNR curve in \eqref{eq:SNRdef}:
%
\begin{equation}\label{eq:laplacedef}
  A(s) = \intd[_0^\infty]{t} \e^{-st} \snr(t),
  \qquad
  \snrb(\tau) = \frac{A(1/\tau)}{\tau}.
\end{equation}
%

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s \I + \onev \arow -\MM)\inv,
\end{equation}
%
where \(\arow\) is an arbitrary row vector satisfying \(\arow \onev = \frac{1}{\tau_0} \neq 0\).
This reduces to the fundamental matrix at \(s=0\).
We can see that it obeys similar identities, including that \(\onev\) is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
\begin{aligned}
  \fund(s) \onev &= \frac{\tau_0}{1+s\tau_0}\onev, \qquad &
  \MM \fund(s) &= (\onev \eq - \I)(\I - s \fund(s)), \\ 
  \arow \fund(s) &= \eq (\I - s \fund(s)),  &
  \fund(s) \MM &= (\I - s \fund(s))(\tau_0 \onev \arow - \I).
\end{aligned}
\end{equation}
%
Suppose we have some row vector \(\mathbf{a}\) such that \(\mathbf{a}\onev=0\).
Then \(\mathbf{a}\fund(s)\) is independent of \(\arow\):
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\arowm_k} = -(\mathbf{a}\fund(s)\onev) \fundm_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fundm_{ki}(s) = 0.
\end{equation}
%

@@

At other values of \(s\) can they be interpreted as the mean first-passage times of a different process?
In order to have \cref{eq:lfund} as its fundamental matrix, the extra bit must draw probability from each state at a rate \(s\).
In other words, it should have the form \(s(\onev \boldsymbol{\zeta} - \I)\) for some \(\boldsymbol{\zeta} \) 
(which can be absorbed into \(\arow\) in \cref{eq:lfund}).
This other process must have the same steady-state distribution, so that its mean first-passage times are given by \cref{eq:lfptb}, so the probability drawn from each state must be redistributed proportional to \(\eq\).
This other stochastic process is
%
\begin{equation}\label{eq:lshift}
  \shift{\MM}(s) = \MM + s (\onev \eq - \I).
\end{equation}
%
This is a valid continuous-time Markov process.
Its fundamental matrix is given by \cref{eq:lfund} with \( \arow(s) = \arow - s \eq \) (although this last change is unnecessary).

The usual fundamental matrix identities will hold provided we use \cref{eq:lshift} as the transition matrix and we note that the \( \arow \) we used should be interpreted as \( \arow(s)\) and the ``original'' \( \arow \) is \( \arow + s \eq \equiv \shift{\arow}\) and the ``original'' \( \frac{1}{\tau_0} \) is \( \frac{1}{\tau_0} + s \equiv \frac{1}{\shift{\tau}_0}\).
We could rewrite \cref{eq:lfundrowsum} as
%
\begin{equation}\label{eq:lshiftrowsum}
\begin{aligned}
  \fund(s) \onev &= {\shift{\tau}_0}\onev, \qquad &
  \shift{\MM}(s) \fund(s) &= \onev \eq - \I, \\ 
  \shift{\arow} \fund(s) &= \eq,  &
  \fund(s) \shift{\MM}(s) &= \shift{\tau} \onev \shift{\arow} - \I.
\end{aligned}
\end{equation}
%

This means that the \( \fptb(s) \) have all the same properties as in the case \(s=0\).
This includes non-negativity and all of the triangle inequalities.
Identities involving mean first-passage times and the transition matrix will also hold, provided that \cref{eq:lshift} is used as the transition matrix.
In particular, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptbm_{ij}(s) \eqm_j
\end{equation}
%
is independent of the starting state \(i\), but now \(\eta(s) = \tr\fund(s) - \frac{\tau_0}{1 + s \tau_0}\).
We can then define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptbm_{ij}(s) \eqm_j \prn{\frac{1 \pm \wm_j}{2}} 
      =  \sum_{j\in \pm} \fptbm_{ij}(s) \eqm_j.
\end{equation}
%
We can arrange the states in order of decreasing \(\eta^{+}_i(s)\) or increasing \(\eta^{-}_i(s)\).
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etwm_i(s) = \sum_j \fptbm_{ij}(s)\eqm_j \wm_j
    = \eta^+_i(s) - \eta^-_i(s) 
    = 2\eta^+_i(s) - \eta(s) 
    = \eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing \(\etwm_i(s)\) is the same as the order of decreasing \(\eta^{+}_i(s)\) or increasing \(\eta^{-}_i(s)\).
The \(\etwm_i(s)\) can still be used when \(\w\) takes more than two values.

@@

@@

In analogy with the case \(s=0\) in \cite{Lahiri2013synapse}, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= \sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= \sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      % = \sum_k \eqm_k {c}_k(s) \wm_k
      = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) wlg.),s the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

@@

\section{Finite time topology}\label{sec:finite}

Now we'll maximise \(\snrb(\tau)\) for some fixed \(\tau\), subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding \(\eq\w\) fixed.
We can maximise the ratio \wrt \(\eq\w\) later.
From this point on, we work in units where \(r = 1\).

Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(s) - \etwm_j(s))
        +\sum_{\nu i j} { f^\nu \mu^\nu_{ij} \MMdm^\nu_{ij} }
        + \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta\pr\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(f^\nu\) for later convenience.

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{\mathbf{c}_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \MMdm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \MMdm^\nu_{ij} 
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii}) = \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\phantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  &\text{where} \quad 
  \alb^\nu(s) = (\MMd^\nu - \I) \thb(s), \qquad
  \omb^\nu(s) = (\MMd^\nu - \I) \etw(s).
\end{aligned}
\end{equation}
%
If we note that we can write \( \MMd^\nu - \I = \prn{\frg + (-1)^\nu \enc} / 2f^\nu \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{gathered}
  \alb^\nu(s) = \frac{\delta \mathbf{a}(s) + (-1)^\nu \enc \thb(s)}{2f^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta \w + s \delta \etw(s) - (-1)^\nu \mathbf{a}(s)}{2 f^\nu}, \\
\begin{aligned}
  \mu^\nu_{mm} &= - \frac{\eqm_m}{2f^\nu} 
    \left[ 
      c_m(s) (\delta \wm_m + s \delta \etwm_m(s)) - \hat{A}(s)
      + \lambda \delta w_m
      \right. \\ &\phantom{= - \frac{\eqm_m}{2f^\nu} []}\left.
      + (-1)^\nu \prn{ 
        [\encm \thbm(s)]_m - c_m(s) a_m(s)
        + \delta \wm_m + s \delta \etwm_m(s)
        - \lambda a_m(0)
      }
    \right], \\
\end{aligned}
\end{gathered}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

\begin{figure}[tbp]
  \centering
  % Requires \usepackage{graphicx}
  \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=7]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=13]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=21]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=27]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=36]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=50]{envelope.pdf}}
  \end{myenuma}
  \caption[Optimal models]{The models that constitute the numeric envelope in \cref{fig:envnum}.
  The plot to the left of each frame indicates the memory curve of the model shown to the right in green, with the numeric envelope for models with the serial topology in orange and the proven envelope, \eqref{eq:env}, in blue.
  Above the left plot we have a graphical display of the model, described with more detail to the right.
  The area of each node is proportional to the steady state probability in that state and the thickness of the red and blue edges are proportional to the transition probabilities under potentiation and depression.
  The bar graph in the upper right of each frame indicates the transition probabilities from the state to the left of each bar to the state on its right, under potentiation.
  The bar graph in the lower right of each frame indicates the transition probabilities from the state to the right of each bar to the state on its left, under depression.
  The heat map in the centre right of each frame indicates the equilibrium probability distribution for each state.
  See the video for the full set of models.}\label{fig:envvid}
\end{figure}

\subsection{Topology constraining perturbations}\label{sec:topology}

In this section we will see how far we can get in constraining the topology, 
despite the lack of scale invariance.

\subsubsection{Number of exits}\label{sec:exit}

Let us define the following
%
\begin{equation}\label{eq:degenerate}
  \dgn_{m} = \thb + c_m \etw,
  \quad
  \dgn^\nu_m = \dgn_m + (-1)^\nu \etw,
  \quad \implies \;
  \frac{1}{f^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n}) + \mu^\nu_{mn} - \mu^\nu_{mm}.
\end{equation}
%
They should be thought of as collections of vectors rather than matrices.

Suppose that a state \(n\) has a nonzero transition rate from state \(m\) for one \(\nu\).
Then \(\mu^\nu_{mn} = 0\) and:
%
\begin{equation}\label{eq:oneexit}
  \MMdm^\nu_{mn} > 0
  \quad \implies \quad
  \mu^\nu_{mm} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n})
  \quad \implies \quad
  \dgnm_{m,m} - \dgnm_{m,n} \geq - (-1)^\nu (\etwm_m - \etwm_n).
\end{equation}
%
If both \(\nu\) have nonzero rates from \(m\) to \(n\):
%
\begin{equation}\label{eq:doubleexit}
  \MMdm\pot_{mn}, \MMdm\dep_{mn} > 0
  \qquad \implies \qquad
  \dgnm_{m,m} - \dgnm_{m,n} \geq\abs{\etwm_m - \etwm_n}.
\end{equation}
%
